Abstract Binding Trees

### 2015-11-07 paper.tex
[paper] fix bug in interpretation
[paper] typos
Switch to codomain fibration

\newcommand\Cats{\mathbf{Cat}}
\newcommand\Discrete[1]{#1_{\equiv}}
\newcommand\Sets{\mathbf{Set}}
\newcommand\SCtx{\mathbf{SCtx}}
\newcommand\Ctx{\mathbf{Ctx}}
\newcommand\Seq{\mathbf{Seq}}
\newcommand\HypCat{\mathbf{H}}

@@

Then, fix a covariant presheaf (copresheaf) of operators
$\Of{\Operators}{\SCtx\times\Discrete{\Arities}\to\Sets}$ such that the arrows
in $\SCtx$ lift to renamings of operators' parameters. Via the Grothendieck
construction\footnote{In this case, $\mathbf{C}\Grothendieck{}{\Psi}$
  represents the category of elements of a copresheaf
  $\Of{\Psi}{\mathbf{C}\to\Sets}$ but we keep the $\mathbf{C}$ implicit and
  simply refer to it as the Grothendieck construction.  Alternatively, this
  construction can be understood as a coend
$\IMode{\mathbf{C}\Grothendieck{}{\Psi}}\cong \IMode{\int^{c \in
\mathbf{C}}\Coslice{c}{\mathbf{C}} \otimes \Discrete{\Psi(c)}}$.}
$\Of{\Grothendieck{}{(-)}}{\Sets^{\mathbf{C}}\to\Cats}$ on operators, we have a
category of objects
$\Member{\Pair{\Pair{\Upsilon}{a}}{\vartheta}}{\Grothendieck{}{\Operators}}$
for $\Member{\vartheta}{\Operators\Pair{\Upsilon}{a}}$ and morphisms
$\Hom{\Grothendieck{}{\Operators}}{\Pair{\Pair{\Upsilon}{a}}{\vartheta}}{\Pair{\Pair{\Upsilon'}{a'}}{\vartheta'}}$
for $\Of{\Pair{\varrho}{f}}{\Pair{\Upsilon}{a}\to\Pair{\Upsilon'}{a'}}$ such
that
$\EqMember{\FLift{\varrho}{f}(\vartheta)}{\vartheta'}{\Operators\Pair{\Upsilon'}{a'}}$.
Equivalently, $\Grothendieck{}{\Operators}$ is the pullback of $\Operators$
along the universal $\Sets$-bundle where $\pi_{\Operators}$ is a discrete
Grothendieck opfibration and $\Forget{-}_{\SSingleton}$ is the forgetful functor
from pointed sets:

\[
\begin{tikzcd}[ampersand replacement = \&, sep = large]
  {\Grothendieck{}{\Operators}}
    \arrow[r, "{\pi_{\in}}"]
    \arrow[d, "{\pi_{\Operators}}" left]
  \& {\Sets_{\SSingleton}}
    \arrow[d, "{\Forget{-}_{\SSingleton}}"] \\
  {\SCtx\times\Discrete{\Arities}}
     \arrow[r, "{\Operators}" below]
  \& {\Sets} \\
\end{tikzcd}
\]

@@

We will proceed using the initial $\SigFun{\Sigma}$-algebra $\alpha$, as
follows.
\[
   \begin{tikzcd}[ampersand replacement = \&, sep=large]
     {\IMode{\SemBrackets{\Omega\triangleright\Upsilon\parallel\Gamma}_P}} \arrow[r, "\OMode{\beta}"]
     \& {\IMode{\SigFun{\Sigma}(P)_\tau}} \arrow[r, "\IMode{\alpha}"]
     \& {\IMode{P_\tau}}
   \end{tikzcd}
\]

\begin{align*}
  \ADefine{
    \beta
  }{
   \begin{tikzcd}[ampersand replacement = \&, sep=huge]
      {\SemBrackets{\Omega\triangleright\Upsilon\parallel\Gamma}_P} \arrow[r, "\Tuple{\SemBrackets{\vartheta}_P, \gamma}"]
      \& {
        \coprod_{\vartheta\in \Operators_{\MkArity{\vec{v}}{\tau}}}
        \prod_{\MkValence{\vec{\sigma}_i}{\vec{\tau}_i}{\tau_i}\in\vec{v}}
        P_{\tau_i}^{\Yoneda{\vec{\sigma}_i\parallel\vec{\tau}_i}}
      }
   \end{tikzcd}
  }\\
  \ADefine{
    \gamma
  }{
   \begin{tikzcd}[ampersand replacement = \&, sep=6em]
      {\SemBrackets{\Omega\triangleright\Upsilon\parallel\Gamma}_P} \arrow[r, "\Tuple{\lambda x. \eta_i(-,x))}_i"]
      \& {
        \prod_{\MkValence{\vec{\sigma}_i}{\vec{\tau}_i}{\tau_i}\in\vec{v}}
        P_{\tau_i}^{\Yoneda{\vec{\sigma}_i\parallel\vec{\tau}_i}}
      }
   \end{tikzcd}
  }\\
  \ADefine{
    \eta_i
  }{
   \begin{tikzcd}[ampersand replacement = \&, sep=7em]
      {\SemBrackets{\Omega\triangleright\Upsilon\parallel\Gamma}_P
        \times\Yoneda{\vec{\sigma}_i\parallel\vec{\tau}_u}
      } \arrow[r, "\Tuple{\pi_1\circ\pi_1,\phi_i,\nu_{\Gamma,\vec{\tau}_i}\circ\psi_i}"]
      \& {\SemBrackets{\Omega\triangleright\Upsilon,\vec{\sigma}_i\parallel\Gamma,\vec{\tau}_i}_P}
      \arrow[r, "\SemBrackets{\Omega\triangleright\Upsilon,\vec{\sigma}_i\parallel\Gamma,\vec{\tau}_i\vdash M_i:\tau_i}_P"]
      \& {P_{\tau_i}}
   \end{tikzcd}
  }\\
  \ADefine{
    \phi_i
  }{
   \begin{tikzcd}[ampersand replacement = \&, sep=12em]
      {\SemBrackets{\Omega\triangleright\Upsilon\parallel\Gamma}_P
        \times\Yoneda{\vec{\sigma}_i\parallel\vec{\tau}_u}
      } \arrow[r, "\Tuple{\pi_u\circ\pi_1}_{u\in\Dom\Upsilon}\oplus\Tuple{\pi_u\circ\pi_1\circ\pi_2}_{u\in\Dom{\vec{\sigma}_i}}"]
      \& {S^{\{\Upsilon,\vec{\sigma}_i\}}}
   \end{tikzcd}
  }\\
  \ADefine{
    \psi_i
  }{
   \begin{tikzcd}[ampersand replacement = \&, sep=12em]
      {\SemBrackets{\Omega\triangleright\Upsilon\parallel\Gamma}_P
        \times\Yoneda{\vec{\sigma}_i\parallel\vec{\tau}_u}
      } \arrow[r, "\Tuple{\pi_u\circ\pi_1}_{u\in\Dom\Upsilon}\oplus\Tuple{\pi_u\circ\pi_1\circ\pi_2}_{u\in\Dom{\vec{\sigma}_i}}"]
      \& {V^{[\Gamma,\vec{\tau}_i]}}
   \end{tikzcd}
  }
\end{align*}

>>>>

\newcommand\Cats{\mathbf{Cat}}
\newcommand\Discrete[1]{#1_{\equiv}}
\newcommand\Arr[1]{\mathbf{{#1}^{\rightarrow}}}
\newcommand\Sets{\mathbf{Set}}
\newcommand\SCtx{\mathbf{SCtx}}
\newcommand\Ctx{\mathbf{Ctx}}
\newcommand\Seq{\mathbf{Seq}}
\newcommand\HypCat{\mathbf{H}}

@@

Then, fix a covariant presheaf (copresheaf) of operators
$\Of{\Operators}{\SCtx\times\Discrete{\Arities}\to\Sets}$ such that the arrows
in $\SCtx$ lift to renamings of operators' parameters. Via the Grothendieck
construction\footnote{In this case, $\mathbf{C}\Grothendieck{}{\Psi}$ represents
  the category of elements of a copresheaf $\Of{\Psi}{\mathbf{C}\to\Sets}$ but
  we keep the $\mathbf{C}$ implicit and simply refer to it as the Grothendieck
  construction. Alternatively, this construction can be understood as a coend
  $\IMode{\mathbf{C}\Grothendieck{}{\Psi}}\cong \IMode{\int^{c \in
      \mathbf{C}}\Coslice{c}{\mathbf{C}} \otimes \Discrete{\Psi(c)}}$.}
$\Of{\Grothendieck{}{(-)}}{\Sets^{\mathbf{C}}\to\Cats}$ on operators, we have a
category of objects
$\Member{\Pair{\Pair{\Upsilon}{a}}{\vartheta}}{\Grothendieck{}{\Operators}}$ for
$\Member{\vartheta}{\Operators\Pair{\Upsilon}{a}}$ and morphisms
$\Hom{\Grothendieck{}{\Operators}}{\Pair{\Pair{\Upsilon}{a}}{\vartheta}}{\Pair{\Pair{\Upsilon'}{a'}}{\vartheta'}}$
for $\Of{\Pair{\varrho}{f}}{\Pair{\Upsilon}{a}\to\Pair{\Upsilon'}{a'}}$ such
that
$\EqMember{\FLift{\varrho}{f}(\vartheta)}{\vartheta'}{\Operators\Pair{\Upsilon'}{a'}}$.
Equivalently, $\Grothendieck{}{\Operators}$ is the pullback of $\Operators$
along the the codomain Grothendieck bifibration $\pi_{cod}$ where
$\pi_{\Operators}$ is also a discrete Grothendieck opfibration:

\[
\begin{tikzcd}[ampersand replacement = \&, sep = large]
  {\Grothendieck{}{\Operators}}
    \arrow[rr, "{\Pair{\Pair{\Upsilon}{a}}{\vartheta}\ \mapsto\ \ArrId{\Operators\Pair{\Upsilon}{a}}}"]
    \arrow[d, "{\pi_{\Operators}}" left]
  \&
  \& {\Arr{\Sets}}
    \arrow[d, "{\pi_{cod}}"] \\
  {\SCtx\times\Discrete{\Arities}}
     \arrow[rr, "{\Operators}" below]
  \&
  \& {\Sets} \\
\end{tikzcd}
\]

@@

We will proceed using the initial $\SigFun{\Sigma}$-algebra $\alpha$, as
follows.
\[
   \begin{tikzcd}[ampersand replacement = \&, sep=large]
     {\IMode{\SemBrackets{\Omega\triangleright\Upsilon\parallel\Gamma}_P}} \arrow[r, "\OMode{\beta}"]
     \& {\IMode{\SigFun{\Sigma}(P)_\tau}} \arrow[r, "\IMode{\alpha_\tau}"]
     \& {\IMode{P_\tau}}
   \end{tikzcd}
\]

\begin{align*}
  \ADefine{
    \beta
  }{
   \begin{tikzcd}[ampersand replacement = \&, sep=huge]
      {\SemBrackets{\Omega\triangleright\Upsilon\parallel\Gamma}_P} \arrow[r, "\Tuple{\SemBrackets{\vartheta}_P, \gamma}"]
      \& {
        \coprod_{\vartheta\in \Operators_{\MkArity{\vec{v}}{\tau}}}
        \prod_{\MkValence{\vec{\sigma}_i}{\vec{\tau}_i}{\tau_i}\in\vec{v}}
        P_{\tau_i}^{\Yoneda{\vec{\sigma}_i\parallel\vec{\tau}_i}}
      }
   \end{tikzcd}
  }\\
  \ADefine{
    \gamma
  }{
   \begin{tikzcd}[ampersand replacement = \&, sep=6em]
      {\SemBrackets{\Omega\triangleright\Upsilon\parallel\Gamma}_P} \arrow[r, "\Tuple{\lambda x. \eta_i(-,x))}_i"]
      \& {
        \prod_{\MkValence{\vec{\sigma}_i}{\vec{\tau}_i}{\tau_i}\in\vec{v}}
        P_{\tau_i}^{\Yoneda{\vec{\sigma}_i\parallel\vec{\tau}_i}}
      }
   \end{tikzcd}
  }\\
  \ADefine{
    \eta_i
  }{
   \begin{tikzcd}[ampersand replacement = \&, sep=7em]
      {\SemBrackets{\Omega\triangleright\Upsilon\parallel\Gamma}_P
        \times\Yoneda{\vec{\sigma}_i\parallel\vec{\tau}_u}
      } \arrow[r, "\Tuple{\pi_1\circ\pi_1,\phi_i,\psi_i}"]
      \& {\SemBrackets{\Omega\triangleright\Upsilon,\vec{\sigma}_i\parallel\Gamma,\vec{\tau}_i}_P}
      \arrow[r, "\SemBrackets{\Omega\triangleright\Upsilon,\vec{\sigma}_i\parallel\Gamma,\vec{\tau}_i\vdash M_i:\tau_i}_P"]
      \& {P_{\tau_i}}
   \end{tikzcd}
  }\\
  \ADefine{
    \phi_i
  }{
   \begin{tikzcd}[ampersand replacement = \&, sep=12em]
      {\SemBrackets{\Omega\triangleright\Upsilon\parallel\Gamma}_P
        \times\Yoneda{\vec{\sigma}_i\parallel\vec{\tau}_i}
      } \arrow[r, "\Tuple{\pi_u\circ\pi_1}_{u\in\Dom\Upsilon}\oplus\Tuple{\pi_u\circ\pi_1\circ\pi_2}_{u\in\Dom{\vec{\sigma}_i}}"]
      \& {S^{\{\Upsilon,\vec{\sigma}_i\}}}
   \end{tikzcd}
  }\\
  \ADefine{
    \psi_i
  }{
   \begin{tikzcd}[ampersand replacement = \&, sep=12em]
      {\SemBrackets{\Omega\triangleright\Upsilon\parallel\Gamma}_P
        \times\Yoneda{\vec{\sigma}_i\parallel\vec{\tau}_i}
      } \arrow[r, "\Tuple{\pi_x\circ\pi_1}_{x\in\Dom\Gamma}\oplus\Tuple{\pi_x\circ\pi_1\circ\pi_2}_{x\in\Dom{\vec{\tau}_i}}"]
      \& {V^{[\Gamma,\vec{\tau}_i]}}
   \end{tikzcd}
  }
\end{align*}
